The logic course is based on natural deduction.
Proof-editing software, tableau editor.
The first order language has no free variables. Arbitrary and proper names are
indistiguishable.
Every formula makes sense as a sentence on its own, and has a truth value on
interpretation.
Quantifiers are binary operations, rather than unary.
Natural deduction vs semantic tableaux.
Limitations of semantic tableaux: looks complicated when used with quantifiers
and function symbols, hard to used with identity, cannot easily accommondate
non-classical reasonining, do not readily connect with uses of logic as the
basis for axiomatic theories. 
Traditional syllogistic logic is a tiny fragment of a first order language.
Extension vs. alternative.
Glossary.
The webpage has a setting to set up logical notation for the entire webpage via
a preference menu. The same can be done for a Latex document via command
sequences definitions.

Formal logic -> philosophy, mathematics, and computer science.
The focus on the question 'Why?' rather than 'How?'
Conceptual foundations.
"These notes are not bedtime stories: you can't read them with your brain in
neutral."
A problem with linear structures is that they hide more sophisticated and rich
structure that some of them actually have.
Logic is focused on inference and argument.
Sentences of a language are descriptive or indicative sentences which can be
used to describe something or other. A sentence has a truth value. It is either
true or false.
An argument is a set of premises and a conclusion. An argument makes a claim
that the conclusion is true if all the premises are true.
If you accept the truth of all premises you should accept the truth of the
conclusion, and if you deny the conclusion while being aware of the argument you
must be prepared to reject at least one of the premises.
"Logic and logicians cannot compel anyone to be rational ..."

An argument is valid if its conclusion follow logically from its premises.
Demonstration that an argument cannot be a source of an error.

The argument is valid if its impossible for its premises to be true and its
conclusion false. Conversely, an argument is invalid if there is a way for its
premises to be true and its conclusion false.

Arguments can be valid for other reasons other than their form, but logic is
not interested in such arguments.
