\documentclass[letterpaper, 10pt]{article}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
\usepackage{mathtools}
\usepackage{enumitem}

\setlength{\parindent}{0pt}

\theoremstyle{definition}
\newtheorem{thm}{Theorem}[section]
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{define}[thm]{Definition}

\newcommand{\set}[1]{\{#1\}}
\newcommand{\tuple}[1]{\langle #1 \rangle}
\renewcommand{\gcd}[1]{\left( #1 \right)}
\newcommand{\abs}[1]{\left| #1 \right|}
\renewcommand{\cong}[3]{#1 \equiv #2 (mod\ #3)}
\newcommand{\divides}[2]{#1 \mid #2}
\renewcommand{\vec}[1]{\mathbf #1}
\newcommand{\vect}[1]{\overrightarrow{#1}}
\newcommand{\comp}[1]{\overline{#1}}
\newcommand{\powerset}[1]{\mathcal{P}(#1)}
\renewcommand{\implies}{\rightarrow}
\newcommand{\entails}{\vdash}
\newcommand{\bicond}{\leftrightarrow}

\begin{document}

\section{Symbolic language}
\subsection{Statements}

\begin{define}
	Statement is a sentence that is either true or false.
\end{define}

\begin{define}
	Substatement is a part of a statement that could be considered a statement
	on its own.
\end{define}

\begin{define}
	A simple statement is a statement that does not properly contain any
	substatements.
\end{define}

\begin{define}
	A compound statement is a statement that contains two or more substatements.
\end{define}

\begin{define}
	A connective is a connecting word or group of words that connects
	substatements in a compound statement.
\end{define}

The five basic connectives are negation, conjunction, disjunction, conditional
and biconditional.

Given statements $A$ and $B$, we use these connectives to construct new
statements.

When a sentence contains free variables it is not a statement since we cannot
say whether it is true or false, but we can make it one by substituting names of
concrete objects for occurences of free variables in a sentence.

\subsection{Converting language to symbols}

We will use letters to represent logical statements and substatements, and the
symbols $\neg, \land, \lor, \rightarrow, \leftrightarrow$ to represent negation,
conjunction, disjuntion, conditional and biconditioncal connectives,
respectively.

\subsection{Logical Analysis}

We establish the truth tables of the basic connectives.

\begin{define}
	Truth value is the property of being true or false.
\end{define}

Even though there are infinitely many statements that can be assigned to a
statement variables each statement is either true or false. Therefore, in a
logical statement with a finite number of statement variables, there is
a finite number of truth assignments to the variables.

\subsection{Tautologies and contradictions}

\begin{define}
	Tautology is a logical statement that is always true for all possible truth
	values of its variable substatements.
\end{define}

The list of simple tautologies:
\begin{enumerate}
	\item $p \implies p$
	\item $p \bicond p$
	\item $p \vee \neg p$ The law of excluded middle.
	\item $\neg(p \wedge \neg p)$ The law of contradiction.
\end{enumerate}

\begin{define}
	Contradiction is a statement that is always false, regardless of the truth
	values of its variable substatements.
\end{define}

Negation of a tautology is a contradiction and negation of a
contradiction is a tautology.

Implication $A \implies B$ can only be a contradiction if $A$ is a tautology and
$B$ is a contradiction.

\begin{thm}[Substitution Rule]
	Suppose $A$ is a logical statement involving substatement variables
	$p_1,p_2,\ldots,p_m$. If $A$ is logically true or logically false, then so
	is every statement obtained from $A$ by replacing each statement variable
	$p_i$ by some logical statement $B_i$, for every possible collection of
	logical statements $B_1,B_2,\ldots,B_m$.
\end{thm}

\begin{define}
	A statement $A$ logically implies a statement $B$ if the conditional $A
	\implies B$ is a tautology.
\end{define}

\section{Logical equivalence}

\subsection{Equivalence}

\begin{define}
	Statements $A$ and $B$ are logically equivalent if and only $A \bicond B$ is a
	tautology. 
\end{define}

Logical equivalence has the follwoing properties:
\begin{enumerate}
	\item It is reflexive. That is, $A \equiv B$ is true for every $A$.
	\item It is symmetric. That is, whenever $A \equiv B$, then also $B \equiv
		A$.
	\item It is transitive. That is, whenever $A \equiv B$ and $B \equiv C$,
		then also $A \equiv C$.
	\item Every pair of tautologies is an equivalent pair of logical statements.
	\item Every pair of contradictions is an equivalent pair of logical
		statements.
\end{enumerate}

\begin{thm}[Substitution Rules]
	\begin{enumerate}
		\item Replacing a substatement by an equivalent one. Suppose $A$ is a
			logical statement and $X$ is a substatement of $A$. If a statement
			$Y$ is equivalent to $X$, then the new statement $A'$ obtained from
			$A$ by replacing substatement $X$ by $Y$ is equivalent to $A$. That
			is, if $Y \equiv X$ then $A'\equiv A$.
		\item Substituting into a known equivalence. Suppose $A$ and $B$ are
			logical statements, each of which involves substatement variables
			$p_1,p_2,\ldots,p_m$. If $A$ and $B$ are equivalent, then so are new
			statements $A'$ and $B'$ obtained by applying substitution $p_i=C_i$
			to both $A$ and $B$, for every collection of statements
			$C_1,C_2,\ldots,C_m$.
	\end{enumerate}
\end{thm}

\section{Language as an algebra}

We can treat negation and disjuction as operations on the set of sentences of
the propositional calculus. There is associated with the propositional calculus
a natural algebraic structure whose universe is the set of all sentences and
whose operations are negation and disjunction.

A finite sequence is a function $x$ whose domain is the set of natural numbers
smaller than some fixed natural number $n$, that is, the set
$\set{0,\ldots,n-1}$. It is customary to denote the value of $x$ at $i$ by
$x_i$, where $0 \leq i < n$. If $n = 0$, then $x$ is the empty function.

There is a natural binary operation on finite sequences. If $x$ and $y$ are
finite sequences, so is $xy$. If $x$ and $y$ are of lengths $m$ and $n$
respectively, then $xy$ is of length $m + n$. The values of $xy$ are given by
\[
	(xy)_i=
	\begin{cases}
		x_i\quad\textrm{if}\ i < m \\
		y_{i - m}\quad\textrm{if}\ i \geq m \\
	\end{cases}
\]
where $0 \leq i < m + n$. The operation $xy$ is called concatenation. The
operation of concatenation is associative. The set of all non-emtpy finite
sequences of $A$ is called the free semigroup generated by $A$. If we add the
empty sequence to the set above, the semigroup acquires a unit.j


\section{Theorems}

\subsection{Axioms of propositional calculus}

We can specify the set of all axioms of the propositional calculus either using
axiom schemata or by substitution rules.

\begin{enumerate}[label=T\arabic*, left=0pt]
	\item $x \lor x \implies x$.
	\item $x \implies x \lor y$.
	\item $x \lor y \implies y \lor x$.
	\item $(x \implies y) \implies (z\lor x \implies z \lor y)$.
\end{enumerate}

Define a binary operation on the set of all sentences, denoted $\mu$ and called
modus ponens, such that, if $x$ and $z$ are sentences and if $z$ has the form $x
\implies y$, then $\mu(x,z) = y$, otherwise $\mu(x,z) = x$.
The sentence $y$ is a theorem if and only if there exists a finite sequence of
sentences, whose last term is $y$, such that each sentence in the sequence is
either an axiom, or the result of applying modus ponens to some pair of
preceding sentences in the sequence. A finite sequence with these properties is
called a proof (a formal proof, a formal proof of $y$).

\section{Formal proofs}

\begin{enumerate}[label=T\arabic*, left=0pt, resume]
	\item $\entails (x \implies y) \implies ((z \implies x) \implies (z \implies
		y))$,
	\item $x \implies x$,
	\item $x \lor \neg x$,
	\item $\entails x \implies x \lor x$,
	\item $\entails x \implies y \lor x$, 
	\item $\entails x \implies \neg \neg x$, 
	\item $\entails \neg \neg x \implies x$, 
	\item $\entails (x \implies y) \implies (\neg y \implies \neg x)$.
\end{enumerate}
\section{Entailment}

Implication is derived binary operation on on the set of sentences of the
propositional logic. It is defined in terms of the primitive operations.

Let us introduce a binary relation, called entailment. If $x$ and $y$ are
sentences, then the relation of entailment, denoted by $x \leq y$, means that $x
\implies y$ is a theorem, that is, $\entails x \implies y$.

\section{Logical equivalence}

We introduce a new binary relation called equivalence (symbolized by $\equiv$).
If $x$ and $y$ are sentences, then
\begin{equation*}
	x \equiv y
\end{equation*}
means, by definition, that $x\ leq y$ and $y \leq x$, that is, that both $x
\implies y$ and $y \implies x$ are theorems.

We shall show that logical equivalence is a congruent relation on the algebra of
sentences, that is, it is compatible with propositional connectives.

\section{Conjunction}

Let us introduce a new propositional connective, as an abbreviation. Let $x$ and
$y$ be sentences, then $x \land y$ means $\neg(\neg x \lor \neg y)$.

Another abbreviation is a bi-implication or biconditional connective. 
Let again $x$ and $y$ be sentences, then $x \bicond y$ means $(x \implies
y)\land (y\implies x)$.

Both conjunction and biconditional are binary operations on the set of all
sentences of the propositional calculus. They are derived operations in the
sense that they are defined in terms of the basic operations of negation and
disjunction. The relation $\equiv$ is a congruence relation with respect to
conjuction and biconditional.
\end{document}
